---
title: "Inclusiveness Index Data"
author: "Angela Zoss"
date: "3/5/2023"
output: html_document
---

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)
library(here)
here::i_am("Day 1/1-inclusiveness.Rmd")

```

## Load your data

```{r}

# load using included script file

source(here("data", "inclusiveness_index", "load_inclusiveness_index.R"))

```

## Preview the data

```{r, eval=F}

View(inclusiveness_index)

```

## Create a bar chart to explore the data coverage across `Continent`

```{r}

# Remember the basic steps:
# - set the data (main function)
# - choose a shape layer
# - map variables to aesthetics using aes()

# Note: for a bar chart, you just need to specify the x-axis



```

## Add a new aesthetics mapping to *fill* the bars according to `Index.categories.2020`

```{r}



```

## Create a histogram to explore the distribution of `Inclusiveness.index.2020`

Before we start, what is the difference between a bar chart and a histogram?

```{r}



```

## Add a new aesthetics mapping to *fill* the bins according to `Index.categories.2020`

```{r}



```

## Create a scatter plot comparing `Z.score.Religion` to `Inclusiveness.index.2020`

```{r}



```

## Add a new aesthetics mapping to *color* the points by `Continent`


```{r}



```

## Review slides on creating repeated charts

## Advanced: Split scatterplot into multiple charts, one per Continent

```{r}

# Hint: check the help page for facet_wrap()



```

## Review slides on helpful data manipulation

## Advanced: Bar charts, column charts, and calculations

```{r}

# geom_bar() has a summary function built in

ggplot(data = inclusiveness_index) +
  geom_bar(mapping = aes(x = Continent))

```

```{r}

# Use count() to create a tibble with the same summarized data from the bar chart.



```

```{r}

# geom_col() creates a bar chart, but instead of summarizing the data for you it
# takes both an x value and a y value. Use the data from the count() summary
# and the geom_col() shape layer to create a bar chart this other way.



```

```{r}

# Now calculate a different summary number for each continent: average inclusiveness index.
# Visualize the results with geom_col().



```