---
title: "Inclusiveness Index Data"
author: "Angela Zoss"
date: "8/1/2022"
output: html_document
---

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)

```

## Load your data

```{r}

# load using included script file

source('../data/inclusiveness_index/load_inclusiveness_index.R')

```

## Preview the data

```{r}

View(inclusiveness_index)

```


## Create a bar chart to explore the data coverage across `Continent`


```{r}

# Remember the basic steps:
# - set the data (main function)
# - choose a shape layer
# - map variables to aesthetics using aes()

# Note: for a bar chart, you just need to specify the x-axis

ggplot(data = inclusiveness_index,
       mapping = aes(x = Continent)) +
  geom_bar()

```

## Add a new aesthetics mapping to fill the bars according to `Index.categories.2020`

```{r}

ggplot(data = inclusiveness_index,
       mapping = aes(x = Continent,
                     fill = Index.categories.2020)) +
  geom_bar()

```


## Create a histogram to explore the distribution of the 2020 Inclusive Index scores

```{r}

# hint: Inclusiveness.index.2020 is numerical; 
# look for geoms that do a good job of summarizing numerical variables

ggplot(data = inclusiveness_index, 
       mapping = aes(x = Inclusiveness.index.2020)) +
  geom_histogram()

```

## Create a histogram to explore the distribution of the 2020 Inclusive Index scores

```{r}

ggplot(data = inclusiveness_index, 
       mapping = aes(x = Inclusiveness.index.2020,
                     fill = Index.categories.2020)) +
  geom_histogram()

```

## Create a scatter plot comparing `Z.score.Religion` to `Inclusiveness.index.2020`

```{r}

ggplot(data = inclusiveness_index,
       mapping = aes(x = Z.score.Religion,
                     y = Inclusiveness.index.2020)) +
  geom_point() 

```

## Add a new aesthetics mapping to color the points by `Continent`

```{r}

ggplot(data = inclusiveness_index,
       mapping = aes(x = Z.score.Religion,
                     y = Inclusiveness.index.2020,
                     color=Continent)) +
  geom_point() 

```

## Advanced: Split scatterplot into multiple charts, one per Continent

```{r}

# Hint: check the help page for facet_wrap()

ggplot(data = inclusiveness_index,
       mapping = aes(x = Z.score.Religion,
                     y = Inclusiveness.index.2020,
                     color=Continent)) +
  geom_point() +
  facet_wrap(vars(Continent))

```