---
title: "Game of Thromes Character Ratings"
author: "Angela Zoss"
date: "8/9/2024"
output: html_document
---

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)
library(here)
here::i_am("Day 1/3-got_nyt_final.Rmd")

```

## Load your data

```{r}

# data comes from https://int.nyt.com/newsgraphics/2017/2017-07-17-got-matrix/mean.json
# data based on ratings using tool at https://www.nytimes.com/interactive/2017/08/09/upshot/game-of-thrones-chart.html

got <- read_csv(here("data", "got_ratings.csv"))

```

## Create a scatterplot of `moral` vs. `physical`

```{r}

ggplot(data = got) + 
  geom_point(mapping = aes(x=moral,y=physical))

```


## Set the alpha aesthetic (which controls transparency) for all points to .75

```{r}

# check ?geom_point to see names of the different options available
# where should the new option go? what layer? inside or outside of aesthetics?

ggplot(data = got) + 
  geom_point(mapping = aes(x=moral,y=physical), alpha=.75)

```

## Add a new geom that will display labels for each point

```{r}

# hint: check https://ggplot2.tidyverse.org/reference/#section-geoms for all geom options

# wrong way: aes() in geom_point does not carry down; has to be in ggplot() or in both geom layers

#ggplot(got) +
#  geom_point(aes(x=moral,y=physical)) + 
#  geom_text(aes(label=label))

ggplot(data = got) + 
  geom_point(mapping = aes(x=moral, y=physical, alpha=.75)) + 
  geom_text(mapping = aes(x=moral, y=physical, label=label))

```

## Adjust label position to limit overlap with points

```{r}

# hint: look at ?geom_text for an option that might change the position slightly
# where should the new option go? what layer? inside or outside of aesthetics?

ggplot(data = got) + 
  geom_point(mapping = aes(x=moral, y=physical, alpha=.75)) + 
  geom_text(mapping = aes(x=moral, y=physical, label=label), nudge_y = -.025)

```

## Inheritance: Add colors

```{r}

# add gender as a color three different ways:
# - points only
# - labels only
# - both

ggplot(got, aes(x=moral,y=physical)) + 
  geom_point(aes(color=gender), alpha=.75) + 
  geom_text(aes(label=label), nudge_y = -.025)

ggplot(got, aes(x=moral,y=physical)) + 
  geom_point(alpha=.75) + 
  geom_text(aes(label=label, color=gender), nudge_y = -.025)

ggplot(got, aes(x=moral,y=physical, color=gender)) + 
  geom_point(alpha=.75) + 
  geom_text(aes(label=label), nudge_y = -.025)

```

## Turn off legend for text layer

```{r}

# hint: there is another property for the geom_text layer that might help

ggplot(got, aes(x=moral,y=physical, color=gender)) + 
  geom_point(alpha=.75) + 
  geom_text(aes(label=label), nudge_y = -.025, show.legend = FALSE)

```

## Change the theme

```{r}
# Try to find a theme closer to the NYT chart;
# see https://ggplot2.tidyverse.org/reference/#section-themes for built-in themes

ggplot(got, aes(x=moral,y=physical, color=gender)) + 
  geom_point(alpha=.75) + 
  geom_text(aes(label=label), nudge_y = -.025, show.legend = FALSE) +
  theme_minimal()

```

## Add reference lines

```{r}
# hint: there are special geoms for straight lines;
# check https://ggplot2.tidyverse.org/reference/#section-layer-geoms for all geom options

# hint: look at how ggplot2 is layering the plot; rearrange layers as needed

ggplot(got, aes(x=moral,y=physical, color=gender)) + 
  scale_y_reverse() +
  geom_hline(yintercept=.5) +
  geom_vline(xintercept=.5) + 
  geom_point(alpha=.75)  + 
  geom_text(aes(label=label), nudge_y = -.025, show.legend = FALSE) +
  theme_minimal()

```

For more customizations, see https://gist.github.com/amzoss/f9e94e16914e2d04a8fc48810519dc3c