---
title: "Inclusiveness Index Data"
author: "Angela Zoss"
date: "8/7/2021"
output: html_document
---

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)

```

## Load your data

```{r}

# load using included script file

source('../data/inclusiveness_index/load_inclusiveness_index.R')


```

## Create a plot to explore the distribution of the 2020 Inclusive Index scores

```{r}

# hint: Inclusiveness.index.2020 is numerical; 
# look for geoms that do a good job of summarizing numerical variables


```

## Facets: Add a facet to the chart to create small multiples for each continent

```{r}

# hint: try facet_wrap


```

## Create a new plot to compare the Z-score for Religion to the 2020 Inclusiveness Index

```{r}

# what geom is best for two numerical variables?


```

```{r}

# Cleaning up the data: limiting the columns and removing NAs

scatter <- inclusiveness_index %>% 
  dplyr::select(Country, Continent, Z.score.Religion, Inclusiveness.index.2020) %>% 
  drop_na()


```


## Data inheritance: Add a label to (only) the most inclusive country

```{r}

# hint: you can use "data=" in a geom layer to use different data for that layer 

most_inclusive_country <- 
  

```

## Advanced: Add a linear trend line

```{r}

# hint: look at the options for geom_smooth



```

## Advanced: Color (just) the points by Continent

```{r}



```

## Advanced: Separate and color the linear trend line by Continent

```{r}




```

