---
title: "Inclusiveness Index Data"
author: "Angela Zoss"
date: "8/7/2021"
output: html_document
---

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)

```

## Load your data

```{r}

# load using included script file

source('data/inclusiveness_index/load_inclusiveness_index.R')


```

## Create a plot to explore the distribution of the 2020 Inclusive Index scores

```{r}

# hint: Inclusiveness.index.2020 is numerical; 
# look for geoms that do a good job of summarizing numerical variables

ggplot(inclusiveness_index) +
  geom_histogram(aes(Inclusiveness.index.2020))

ggplot(inclusiveness_index) +
  geom_density(aes(Inclusiveness.index.2020))

```

## Facets: Add a facet to the chart to create small multiples for each continent

```{r}

# hint: try facet_wrap

ggplot(inclusiveness_index) +
  geom_histogram(aes(Inclusiveness.index.2020)) + 
  facet_wrap(vars(Continent))

```

## Create a new plot to compare the Z-score for Religion to the 2020 Inclusiveness Index

```{r}

# what geom is best for two numerical variables?

ggplot(inclusiveness_index, 
       aes(x = Z.score.Religion, 
           y = Inclusiveness.index.2020)) +
  geom_point()

```

```{r}

# Cleaning up the data: limiting the columns and removing NAs

scatter <- inclusiveness_index %>% 
  dplyr::select(Country, Continent, Z.score.Religion, Inclusiveness.index.2020) %>% 
  drop_na()


```


## Data inheritance: Add a label to (only) the most inclusive country

```{r}

# hint: you can use "data=" in a geom layer to use different data for that layer 

most_inclusive_country <- scatter %>%
  dplyr::filter(Inclusiveness.index.2020 > 1.2)

most_inclusive_country <- scatter %>%
  dplyr::filter(Inclusiveness.index.2020 == max(Inclusiveness.index.2020, na.rm=TRUE))

ggplot(scatter, 
       aes(x = Z.score.Religion, 
           y = Inclusiveness.index.2020)) +
  geom_point() +
  geom_text(data = most_inclusive_country, aes(label = Country), nudge_y = -.1)

```

## Advanced: Add a linear trend line

```{r}

# hint: look at the options for geom_smooth

ggplot(scatter, 
       aes(x = Z.score.Religion, 
           y = Inclusiveness.index.2020)) +
  geom_point() +
  geom_text(data = most_inclusive_country, aes(label = Country), nudge_y = -.1) +
  geom_smooth(method = "lm", se=FALSE)

```

## Advanced: Color (just) the points by Continent

```{r}

ggplot(scatter, 
       aes(x = Z.score.Religion, 
           y = Inclusiveness.index.2020)) +
  geom_point(aes(color=Continent)) +
  geom_text(data = most_inclusive_country, aes(label = Country), nudge_y = -.1) +
  geom_smooth(method = "lm", se=FALSE)


```

## Advanced: Separate and color the linear trend line by Continent

```{r}

ggplot(scatter, 
       aes(x = Z.score.Religion, 
           y = Inclusiveness.index.2020,
           color=Continent)) +
  geom_point() +
  geom_text(data = most_inclusive_country, aes(label = Country), nudge_y = -.1) +
  geom_smooth(method = "lm", se=FALSE) +
  facet_wrap(vars(Continent))


```

