---
title: "Star Wars Character Data"
author: "Angela Zoss"
date: "8/12/2018"
output: github_document
---

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)

```

## Load your data

```{r}

# built-in data

starwars_chars <- starwars

```

## Create a plot to explore the height of Star Wars characters

```{r}

# hint: height is numerical; 
# look for geoms that do a good job of summarizing numerical variables


```

## Compare character heights to weights (masses)

```{r}

# what geom is best for two numerical variables?


```

## Add a linear trend line

```{r}


```


## Add a label to (only) the heaviest character

```{r}

# hint: you can use "data=" in a geom layer to use different data for that layer 


```

## Add a label to (only) the shortest character

```{r}


```

## Add a facet to the chart to create small multiples for each species

```{r}

# hint: try facet_wrap


```

## Plot each character by their age (birth_year)

```{r}

# hint: many characters have NA for birth_year;
# try removing those characters before plotting


```

## Sort the characters by their age

```{r}

# hint: the forcats package (which is included in tidyvers) 
# has a useful function called fct_reorder that can be used on factors


```

## Relabel the axes if they are difficult to read

```{r}




```

## Create another exploratory chart using at least three variables

```{r}


```
