---
title: "Star Wars Opinion Data"
author: "Angela Zoss"
date: "8/12/2018"
output: github_document
---

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)

```

## Load your data

```{r}

# data from https://fivethirtyeight.com/features/americas-favorite-star-wars-movies-and-least-favorite-characters/
# note: CSV has two rows of headers, so I have manually created a list of headers and am adding
# that after loading just the data rows

new_names <- read_csv('data/StarWarsNames.csv') %>% select(NewNames)
  
starwars_opins <- read_csv('data/StarWars.csv', skip=2, col_names=FALSE) %>% setNames(unlist(new_names))

```

## What percentage of survey participants responded "No" to "SeenAnyYN"?

```{r}

# start with a bar chart


```


```{r}

# change it to a stacked bar chart, where the answers are different colors
# hint: there will only be one bar, so x will no longer be tied to a variable


```

```{r}

# change the coordinate system to polar with theta="y"


```

## Advanced 1: Compare this pattern across genders

```{r}



```

## Advanced 2: Calculate percentage and add as a label, simplify theme

```{r}



```



## Plot the opinions for Hans Solo

```{r}

# hint: there is a geom that will take a categorical variable and count the data points in
# each category
# also: feel free to remove NAs


```

## Plot the opinions for Jar Jar Binks

```{r}


```

## Edit the axes of each of these charts to make them comparable

```{r}

# remember, editing an axis usually requires a scale



```

## Advanced: can you think of another way to standardize the axes?

```{r}



```

## Reorder the opinion levels so they are in a logical order

```{r}

opinion.levels <- c("Unfamiliar (N/A)","Very unfavorably","Somewhat unfavorably",
                    "Neither favorably nor unfavorably (neutral)",
                    "Somewhat favorably","Very favorably")


```

## Flip the axes so the opinion levels are on the y-axis

```{r}


```

## Use a different color for each opinion level

```{r}


```

## Customize the color palette

```{r}

# hint: editing colors requires a change of scale
# can google "R colors" for a list of all named colors



```
