---
title: "Star Wars Opinion Data"
author: "Angela Zoss"
date: "8/12/2018"
output: github_document
---

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)

```

## Load your data

```{r}

# data from https://fivethirtyeight.com/features/americas-favorite-star-wars-movies-and-least-favorite-characters/
# note: CSV has two rows of headers, so I have manually created a list of headers and am adding
# that after loading just the data rows

new_names <- read_csv('data/StarWarsNames.csv') %>% select(NewNames)
  
starwars_opins <- read_csv('data/StarWars.csv', skip=2, col_names=FALSE) %>% setNames(unlist(new_names))

```

## What percentage of survey participants responded "No" to "SeenAnyYN"?

```{r}

# start with a bar chart

ggplot(starwars_opins) +
  geom_bar(aes(SeenAnyYN))

```


```{r}

# change it to a stacked bar chart, where the answers are different colors
# hint: there will only be one bar, so x will no longer be tied to a variable

ggplot(starwars_opins) +
  geom_bar(aes(1,fill=SeenAnyYN))

```

```{r}

# change the coordinate system to polar with theta="y"

ggplot(starwars_opins) +
  geom_bar(aes(1,fill=SeenAnyYN)) +
  coord_polar(theta="y")

```

## Advanced 1: Compare this pattern across genders

```{r}

ggplot(starwars_opins) +
  geom_bar(aes(1,fill=SeenAnyYN)) +
  coord_polar(theta="y") +
  facet_grid(.~Gender)

ggplot(starwars_opins) +
  geom_bar(aes(1,fill=SeenAnyYN), position="fill") +
  coord_polar(theta="y") +
  facet_grid(.~Gender)


```

## Advanced 2: Calculate percentage and add as a label, simplify theme

```{r}

ggplot(starwars_opins) +
  geom_bar(aes(1,fill=SeenAnyYN),show.legend = FALSE) +
  coord_polar(theta="y") +
  geom_text(data=starwars_opins %>% count(SeenAnyYN) %>% mutate(total=sum(n),label=paste0(SeenAnyYN,"\n",round(n/total*100,1),"%")),aes(c(1,1),c(1050,450),label=label)) +
  theme_void() +
  labs(title="Have you seen any of the 6 films in the Star Wars franchise?")

```



## Plot the opinions for Hans Solo

```{r}

# hint: there is a geom that will take a categorical variable and count the data points in
# each category
# also: feel free to remove NAs

ggplot(starwars_opins %>% filter(!is.na(OpinionSolo))) +
  geom_bar(aes(OpinionSolo))

```

## Plot the opinions for Jar Jar Binks

```{r}

ggplot(starwars_opins %>% filter(!is.na(OpinionJarJar))) +
  geom_bar(aes(OpinionJarJar))

```

## Edit the axes of each of these charts to make them comparable

```{r}

# remember, editing an axis usually requires a scale

ggplot(starwars_opins %>% filter(!is.na(OpinionSolo))) +
  geom_bar(aes(OpinionSolo)) +
  scale_y_continuous(limits=c(0,610))

ggplot(starwars_opins %>% filter(!is.na(OpinionJarJar))) +
  geom_bar(aes(OpinionJarJar)) +
  scale_y_continuous(limits=c(0,610))

```

## Advanced: can you think of another way to standardize the axes?

```{r}

ggplot(starwars_opins %>% select(OpinionSolo,OpinionJarJar) %>% gather(character,opinion) %>% na.omit()) +
  geom_bar(aes(opinion)) +
  facet_grid(.~character)

```

## Reorder the opinion levels so they are in a logical order

```{r}

opinion.levels <- c("Unfamiliar (N/A)","Very unfavorably","Somewhat unfavorably",
                    "Neither favorably nor unfavorably (neutral)",
                    "Somewhat favorably","Very favorably")

ggplot(starwars_opins %>% select(OpinionSolo,OpinionJarJar) %>% gather(character,opinion) %>% na.omit() %>% mutate(opinion=factor(opinion, opinion.levels))) +
  geom_bar(aes(opinion)) +
  facet_grid(.~character)

```

## Flip the axes so the opinion levels are on the y-axis

```{r}

ggplot(starwars_opins %>% select(OpinionSolo,OpinionJarJar) %>% gather(character,opinion) %>% na.omit() %>% mutate(opinion=factor(opinion, opinion.levels))) +
  geom_bar(aes(opinion)) +
  facet_grid(.~character) +
  coord_flip()

```

## Use a different color for each opinion level

```{r}

ggplot(starwars_opins %>% select(OpinionSolo,OpinionJarJar) %>% gather(character,opinion) %>% na.omit() %>% mutate(opinion=factor(opinion, opinion.levels))) +
  geom_bar(aes(opinion,fill=opinion),show.legend = FALSE) +
  facet_grid(.~character) +
  coord_flip()

```

## Customize the color palette

```{r}

# hint: editing colors requires a change of scale
# can google "R colors" for a list of all named colors

ggplot(starwars_opins %>% select(OpinionSolo,OpinionJarJar) %>% gather(character,opinion) %>% na.omit() %>% mutate(opinion=factor(opinion, opinion.levels))) +
  geom_bar(aes(opinion,fill=opinion),show.legend = FALSE) +
  facet_grid(.~character) +
  coord_flip() +
  scale_fill_manual(values = c("grey50","firebrick4","firebrick1","grey85","dodgerblue1","dodgerblue4")) +
  theme_minimal()

```
