---
title: "Interactive charts with plotly"
author: "Angela Zoss"
date: "8/8/2021"
output: html_document
---

Plotly is a tool that makes it easy to create interactive charts. There is a web version of plotly, as well as packages for R and Python.

In R, plotly works nicely with R Markdown files, which are files that seamlessly blend R code and other visual content like text and images. R Markdown files can be compiled (or "knit") into a variety of formats. When you have interactive plotly charts, you can knit the R Markdown file to an HTML document that can be shared directly with others or hosted on a website.

```{r setup, echo=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)
library(plotly)

#install.packages("maps")
library(maps)

#install.packages("mapproj")
library(mapproj)

#install.packages("sf")
library(sf)


```

## Game of Thrones Data Exploration

```{r}

# data comes from https://int.nyt.com/newsgraphics/2017/2017-07-17-got-matrix/mean.json
# data based on ratings using tool at https://www.nytimes.com/interactive/2017/08/09/upshot/game-of-thrones-chart.html

got <- read_csv("data/got_ratings.csv")

got_expl <- ggplot(got, aes(x=moral,y=physical, color=gender)) + 
  geom_point(alpha=.75) + 
  geom_text(aes(label=label), nudge_y = -.015, show.legend = FALSE)

got_expl

```


```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart



```

```{r}

# building the chart natively in plotly
# what differences do you notice?

# https://plotly.com/r/text-and-annotations/#styling-text

plot_ly(data = got, x = ~moral, y = ~physical, color = ~gender) %>%
  add_markers() %>%
  add_text(textposition = "bottom center", text = ~label, showlegend = FALSE)

```

## Git Experience Data

```{r}

# built-in data

source('data/git_experience/load_git_experience.R')

git_bar <- git_experience %>%
                   drop_na(first_vcs) %>%
                   mutate(first_vcs = as_factor(first_vcs) %>% 
                       fct_infreq()) %>%
            ggplot(aes(x=first_vcs, fill=first_vcs)) +
              geom_bar()

git_bar

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart



```

```{r}

# finish the plot_ly call to recreate the chart natively
# note: plotly does not automatically create a count when building a bar chart

# Hint: https://plotly.com/r/bar-charts/#mapping-a-color-variable

git_experience %>%
  drop_na(first_vcs) %>%
  mutate(first_vcs = as_factor(first_vcs) %>% 
           fct_infreq()) %>%
  count(first_vcs) %>%
  plot_ly(x = ~..., y = ~..., color = ~ ..., type = 'bar')

```

```{r}

git_line <- git_experience %>% count(year_vcs, first_vcs) %>%
  ggplot(aes(x=year_vcs, y=n, color=first_vcs)) +
    geom_line()

git_line

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart



```

```{r}

# finish the plot_ly call to recreate the chart natively
# Note: in plotly, a line chart is a special kind of scatter plot

# Hint: https://plotly.com/r/line-charts/#

git_experience %>% count(year_vcs, first_vcs) %>%
  plot_ly(x = ~..., y = ~..., color = ~..., type = 'scatter', mode = 'lines')

```

## Inclusiveness Index Data

```{r}

source('data/inclusiveness_index/load_inclusiveness_index.R')

incl_hist <- ggplot(inclusiveness_index) +
  geom_histogram(aes(Inclusiveness.index.2020))

incl_hist

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart



```

```{r}

# finish the plot_ly call to recreate the chart natively
# (add assignments for data and x)

# Hint: https://plotly.com/r/histograms/

plot_ly(data = ..., x = ~..., type = "histogram")

```

```{r}

scatter <- inclusiveness_index %>% 
  dplyr::select(Country, Continent, Z.score.Religion, Inclusiveness.index.2020) %>% 
  drop_na()

most_inclusive_country <- scatter %>%
  dplyr::filter(Inclusiveness.index.2020 == max(Inclusiveness.index.2020, na.rm=TRUE))

incl_scatter <- ggplot(scatter, 
                       aes(x = Z.score.Religion, 
                           y = Inclusiveness.index.2020)) +
                  geom_point(aes(color=Continent)) +
                  geom_text(data = most_inclusive_country, 
                            aes(label = Country), nudge_y = -.1) +
                  geom_smooth(method = "lm", se=FALSE)

incl_scatter

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart



```

```{r}

# try making this one yourself
# hint: you can specify a new dataset for different layers, just like in ggplot2
# also hint: you can calculate a linear model with the following code: 
#   fitted(lm(Inclusiveness.index.2020~Z.score.Religion))
# also also hint: you'll be adding three layers - markers, lines, text
# which is easier - plotly or ggplot2?



```

## Gapminder Average

```{r}

# original chart
# data comes from http://www.gapminder.org/

gap <- read_csv("data/gapminder_avg.csv")
names(gap) <- make.names(names(gap), unique=TRUE)

gap_plot <- ggplot(gap, aes(x=Average.GDP.per.capita, y=Average.Life.expectancy.at.birth)) +
  geom_point(aes(size=Average.Total.population, color=Region)) +
  scale_x_log10() + 
  labs(x="Average GDP per capita (log 10)", y="Average life expectancy at birth", title="Averages across all years of the traditional Gapminder dataset") +
  scale_size_continuous(name="Average total population", breaks=c(7500000,75000000,750000000),labels=c("7.5 million","75 million","750 million")) +
  geom_smooth(method="lm", se=FALSE, color="gray50") +
  geom_text(data=gap %>% filter(Average.Total.population>200000000), aes(label=Country)) +
  theme_bw()

gap_plot

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart


```

```{r}

# Advanced: reproduce the chart in plotly


```

## Mapping with sf

```{r}

nc <- system.file("gpkg/nc.gpkg", package="sf") %>% read_sf() %>% st_transform(32119)

nc_map <- ggplot(nc) +
  geom_sf(aes(fill=BIR74)) +
    scale_fill_gradientn(colors = sf.colors())

nc_map

```


```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart



```


```{r}

# plotly needs a slightly different data load process
nc2 <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)

plot_ly(nc2, split=~NAME, color = ~BIR74, showlegend=F)

```