---
title: "Crosstalk"
author: "Angela Zoss"
date: "8/8/2021"
output: html_document
---

Crosstalk is a package that allows html-based widgets to talk to each other in an R Markdown document. Examples of HTML widgets include interactive charts, maps, and data tables. Crosstalk connects these components to each other by having them pull from a shared dataset. Crosstalk also offers a few interactive filter functions. For basic data exploration, Crosstalk may offer an easier alternative than Shiny, and the output of Crosstalk is simple HTML, which does not require a special server for sharing like Shiny apps do. Simply knit the RMarkdown file into an HTML file, then share the HTML file or host it on a website.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, echo=FALSE)
```

```{r library}

library(tidyverse)
#library(lubridate)
library(DT)
library(plotly)
library(crosstalk)

```

```{r data}

source('data/inclusiveness_index/load_inclusiveness_index.R')

# Wrap data frame in SharedData
shared_incl <- SharedData$new(inclusiveness_index, ~Country.Code)

```

```{r}

incl_hist <- plot_ly(shared_incl, x = ~Inclusiveness.index.2020, type = 'histogram')

incl_scatter <- plot_ly(shared_incl, x = ~Z.score.Religion, y = ~Inclusiveness.index.2020, color = ~Continent)

incl_DT <- DT::datatable(shared_incl, 
                options = list(
              pageLength = 5,
              lengthMenu = c(5, 10, 15, 20)
            ))

```

```{r}

# one feature of crosstalk is the ability to add custom filters to visualizations.
# the options for filters are: 
# - filter_checkbox() # good for a small number of categories
# - filter_slider() # good for numbers, dates
# - filter_select() # good for a larger number of categories, but works like
#     the checkbox because you can still select multiple categories

# crosstalk can arrange elements in both rows and columns. To put two elements
# in a row together, use bscols() and separate each element with a comma.
# to put two elements in the same column (vertically), use list() and
# separate each element with a comma. Rows, columns, and individual elements
# can be nested as needed, but you must always start with bscols(), even
# if you only want one column.

bscols(list(filter_select(id="sel_continent",
              label="Select Continent:",
              sharedData=shared_incl,
              group=~Continent),
       bscols(
         incl_hist,
         incl_scatter
       ),
       incl_DT))

# play with the different filter and chart options to create 
# your own combinations

```

