---
title: "Interactive charts with plotly"
author: "Angela Zoss"
date: "8/5/2022"
output: html_document
---

Plotly is a tool that makes it easy to create interactive charts. There is a web version of plotly, as well as packages for R and Python.

In R, plotly works nicely with R Markdown files, which are files that seamlessly blend R code and other visual content like text and images. R Markdown files can be compiled (or "knit") into a variety of formats. When you have interactive plotly charts, you can knit the R Markdown file to an HTML document that can be shared directly with others or hosted on a website.

```{r setup, echo=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

## Setup your environment

```{r}

# Load required libraries

library(tidyverse)
library(plotly)

library(here)
here::i_am("Day 2/4-plotly-final.Rmd")

```

## Iris

```{r}

iris_scatter <- ggplot(data=iris) +
  geom_point(
     mapping=aes(x=Petal.Width, 
                              y=Petal.Length,
                              color=Species), 
     size=5, alpha=.75)

iris_scatter

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart
# (replace the blanks with the name of the plot)

ggplotly(iris_scatter)

```

```{r}

# build the chart natively in plotly (fill variable names into the blanks)
# what differences do you notice?

plot_ly(
  data = iris, 
  x = ~Petal.Width, 
  y = ~Petal.Length, 
  color = ~Species, 
  type="scatter")

```

## Inclusiveness Index Data

```{r}

source(here("data", "inclusiveness_index", "load_inclusiveness_index.R"))

```

### Bar chart

```{r}

incl_bar <- ggplot(data = inclusiveness_index) +
  geom_bar(mapping = aes(x = Continent))

incl_bar

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart

ggplotly(incl_bar)

```

```{r}

# To use plotly natively, we need to pre-calculate the lengths of the bars.
# The dplyr function count() takes a categorical variable and counts how many
# rows there are for each categorical value.

incl_bar_data <- inclusiveness_index %>%
  count(Continent)

incl_bar_data

```

```{r}

# Now, use the new data set to build the bar chart in plotly. This time, we will
# use type = "bar" instead of type="scatter".

plot_ly(data = incl_bar_data,
        x = ~Continent,
        y = ~n,
        type = "bar"
)

```

```{r}

# This format of the data also works for another chart type - a pie chart.
# Try changing the type to "pie". 

plot_ly(data = incl_bar_data,
        labels = ~Continent,
        values = ~n,
        type = "pie"
)

```


```{r}

# Now, let's try the version with color.

incl_bar_col <- ggplot(data = inclusiveness_index) +
  geom_bar(mapping = aes(x = Continent,
                         fill = Index.categories.2020))

incl_bar_col

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart

ggplotly(incl_bar_col)

```

```{r}

# We still need to pre-calculate the data, but we can't just count the rows
# by continent. We also have to include the Index Categories. The count()
# function can take a series of categorical variables and calculate the count
# for each combination of the values in the columns.

incl_bar_data_color <- inclusiveness_index %>%
  count(Continent, Index.categories.2020)

incl_bar_data_color

```

```{r}

# Now, try to create the plotly version from scratch, use the new data and adding
# the color. There is one additional layer we'll need to add to stack the bars -
# a layout() option called barmode.

plot_ly(data = incl_bar_data_color,
        x = ~Continent,
        y = ~n,
        color = ~Index.categories.2020,
        type = "bar") %>%
  layout(barmode = 'stack')

```

```{r}

# That's funny. When we use plotly directly, the Index Categories get displayed
# in the reverse order. We can adjust that by modifying the order of the factor
# in the dataset.

incl_bar_data_rev <- incl_bar_data_color %>%
  mutate(Index.categories.2020 = fct_rev(Index.categories.2020))

```

```{r}

# Now try exactly the same plotly code you used before. The Index Categories
# should match the ordering in the ggplot2 version now.

plot_ly(data = incl_bar_data_rev,
        x = ~Continent,
        y = ~n,
        color = ~Index.categories.2020,
        type = "bar") %>%
  layout(barmode = 'stack')

```

### Histogram

```{r}

incl_hist <- ggplot(inclusiveness_index) +
  geom_histogram(aes(Inclusiveness.index.2020))

incl_hist

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart

ggplotly(incl_hist)

```

```{r}

# add the plot_ly call to recreate the chart natively, using type = "histogram"
# Hint: you still only need to define one aesthetic (x)

plot_ly(inclusiveness_index, x = ~Inclusiveness.index.2020, type = 'histogram')

```

```{r}

incl_hist_col <- ggplot(data = inclusiveness_index) +
  geom_histogram(mapping = aes(x = Inclusiveness.index.2020,
                               fill = Index.categories.2020))

incl_hist_col

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart

ggplotly(incl_hist_col)

```

```{r}

# Try building a histogram with color in plotly. 
# Hint: What did we have to do to the bar chart when we added color?

plot_ly(inclusiveness_index, 
        x = ~Inclusiveness.index.2020, 
        color = ~Index.categories.2020,
        type = 'histogram') %>%
  layout(barmode = 'stack')

```

```{r}

# In the main plot function, add "nbinsx = 30" to have the bars look more like
# the ggplot2 version. It won't be a perfect match, though, because plotly is
# trying to optimize the histogram bins.

plot_ly(inclusiveness_index, 
        x = ~Inclusiveness.index.2020, 
        color = ~Index.categories.2020,
        type = 'histogram',
        nbinsx = 30) %>%
  layout(barmode = 'stack')

```

### Scatterplot

```{r}

incl_scatter <- ggplot(data = inclusiveness_index) +
  geom_point(mapping = aes(x = Z.score.Religion,
                           y = Inclusiveness.index.2020,
                           color=Continent))

incl_scatter

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart

ggplotly(incl_scatter)

```

```{r}

# Try making this one yourself in plotly.
# What is different about this one, compared to the iris scatterplot?

plot_ly(inclusiveness_index, 
        x = ~Z.score.Religion,
        y = ~Inclusiveness.index.2020,
        color = ~Continent,
        type = "scatter")

```

```{r}

# Adding some changes to geoms, theme, and color palette, we can make a ggplot,
# publication-ready chart that looks like the plotly defaults.

incl_scatter_labs <- ggplot(data = inclusiveness_index) +
  geom_point(mapping = aes(x = Z.score.Religion,
                           y = Inclusiveness.index.2020,
                           color=Continent)) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank()) +
  scale_color_brewer(palette = "Set2")

incl_scatter_labs

```

## Game of Thrones Data Exploration

```{r}

got <- read_csv(here("data","got_ratings.csv"))

got_expl <- ggplot(got, aes(x=moral,y=physical, color=gender)) + 
  geom_point(alpha=.75) + 
  geom_text(aes(label=label), nudge_y = -.025, show.legend = FALSE)

got_expl

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart

ggplotly(got_expl)

```

```{r}

# In plotly, you can add text by adding an add_text() function as a new layer.
# You'll need to specify the text aesthetic in this new layer.

# Some additional properties that might be useful for this layer:
# textposition = "bottom center", showlegend = FALSE

plot_ly(data = got, x = ~moral, y = ~physical, color = ~gender, type = "scatter") %>%
  add_text(text = ~label, textposition = "bottom center", showlegend = FALSE)

```

## Gapminder Average

```{r}

# data comes from http://www.gapminder.org/

gap <- read_csv(here("data","gapminder_avg.csv"))
names(gap) <- c("country","gdp","life.exp","pop","region","color")

gap_plot <- ggplot(gap, aes(x=gdp, y=life.exp)) +
  geom_point(aes(size=pop, color=region)) +
  scale_x_log10(breaks=c(1000,10000)) + 
  labs(x="Average GDP per capita (log 10)", y="Average life expectancy at birth", title="Averages across all years of the traditional Gapminder dataset", color="Region") +
  scale_size_continuous(name="Average total population", breaks=c(7500000,75000000,750000000),labels=c("7.5 million","75 million","750 million")) +
  geom_smooth(method="lm", se=FALSE, color="gray50") +
  geom_text(data=gap %>% filter(pop>200000000), aes(label=country)) +
  theme_bw()

gap_plot

```

```{r}

# use ggplotly() function to convert ggplot2 chart to interactive plotly chart

# Note: There is a difference here! What is missing?

ggplotly(gap_plot)

```

```{r}

# Advanced: reproduce the chart in plotly
# Hints:
# - you'll use add_lines() for the linear trend line, but you'll have to create a model
#   first. There are various ways to do that. Plotly has some examples at:
#   https://plotly.com/r/ml-regression/#linear-regression-with-r
# - using a log scale on an axis is a layout property
# - if you add a text layer, it will inherit the aesthetics mappings from the main plot
#   function; you can cancel out those mappings by mapping the aesthetics to NULL in the
#   new layer

plot_ly(gap, x = ~gdp, y = ~life.exp, size = ~pop, color = ~region, type = "scatter") %>%
  add_lines(y = ~fitted(lm(life.exp~log(gdp))), showlegend = F, line = list(color = '#555555')) %>%
  layout(
    title = list(
      text="Averages across all years of the traditional Gapminder dataset",
      xanchor = 'left',
      x=0
      ),
    legend=list(
      title=list(text='Region')
      ),
    yaxis = list(
      title=list(text='Average life expectancy at birth')
    ),
    xaxis = list(
      title="Average GDP per capita (log 10)",
      type = "log",
      tickvals = list(1000,10000),
      ticktext = list("1000","10000")
      )
    ) %>%
  add_text(data = gap %>% filter(pop > 200000000), size = NULL, color = NULL, text = ~country, textposition="top center", showlegend=F)


```

