---
title: "DT"
author: "Angela Zoss"
date: "8/5/2023"
output: 
  html_document
---

DT is a package that displays data frames in a user-friendly way. It works especially well inside R Markdown documents, which can incorporate "HTML widgets," or little chunks of website that get built from the R script, incorporating datasets and analyses in really interesting ways.

For best results, use knitr to create a fully styled version of this page, rather
than executing individual code chunks.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

```{r library, echo=FALSE}

library(tidyverse)
library(DT)
library(here)
here::i_am("Day 2/5-datatables-final.Rmd")

```

```{r data, echo=FALSE}

source(here("data","inclusiveness_index", "load_inclusiveness_index.R"))

```

## Default DT output

```{r default}

DT::datatable(inclusiveness_index)

```

## Constraining the size

```{r}

DT::datatable(inclusiveness_index,
   options = list(scrollX = TRUE))

```

## Changing DT style with classes

```{r styled}

DT::datatable(inclusiveness_index, 
              class = 'cell-border stripe',
              options = list(scrollX = TRUE))

```

## Changing additional defaults

```{r change-defaults}

DT::datatable(inclusiveness_index, 
              options = list(
                scrollX = TRUE,
                pageLength = 5,
                lengthMenu = c(5, 10, 15, 20)
                )
              )

```

## Adding column filters

```{r column-filters}

DT::datatable(inclusiveness_index, 
              filter = 'top', 
              options = list(
  scrollX = TRUE,
  pageLength = 5,
  lengthMenu = c(5, 10, 15, 20)
))

```

## Turning off global search

```{r no-search}

# see DOM options at https://datatables.net/reference/option/dom

DT::datatable(inclusiveness_index, 
              filter = 'top', 
              options = list(
  scrollX = TRUE,
  pageLength = 5,
  lengthMenu = c(5, 10, 15, 20),
  dom = 'ltip'
))

```
